---
title: "Tampa Report"
subtitle: "COVID-19 Testing Summary"
# author:
#   - name: Garrick Aden-Buie
#     url: "https://garrickadenbuie.com"
#     extra: 
#       - "Moffitt Cancer Center"
#       - "&commat;grrrck"
date: '`r strftime(Sys.time(), "%F %T", tz = "America/New_York")`'
bulma:
  hero: "link"
  hero_button: ["is-outlined"]
  hero_links:
    - name: Github
      url: https://github.com/gadenbuie/covid19-florida
output: 
  bulma::bulma_document:
    pandoc_args: ["--variable", "no-font-awesome"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r library, include=FALSE}
library(dplyr, warn.conflicts = FALSE)
library(tidyr, warn.conflicts = FALSE)
library(readr, warn.conflicts = FALSE)
library(lubridate, warn.conflicts = FALSE)
library(ggplot2, warn.conflicts = FALSE)
library(purrr, warn.conflicts = FALSE)
source(here::here("R/combine-sources.R"))

line_list <- readr::read_csv(here::here("data/covid-19-florida_arcgis_line-list.csv"), guess_max = 1e5)
dash <- readr::read_csv(here::here("data/covid-19-florida_arcgis_summary.csv"), guess_max = 1e5)
doh_ts <- readr::read_csv(here::here("data/covid-19-florida_arcgis_cases-by-day.csv"))

# Test summary import -----------------------------------------------------

testing_summary_dash <- read_csv(here::here("data/covid-19-florida_dash_summary.csv"))

test_summary <-
  combine_scraped_and_api_data(testing_summary_dash, dash)

tampa_test_summary <- 
  dash %>%
  select(timestamp, county = county_1, t_positive, t_total, deaths, t_inconc, c_ed_yes) %>%
  group_by(day = floor_date(timestamp + hours(11), "day")) %>% 
  filter(timestamp == max(timestamp)) %>% 
  ungroup() %>% 
  select(-timestamp, timestamp = day) %>% 
  bind_rows(mutate(., county = "Florida")) %>% 
  filter(county %in% c("Hillsborough", "Pinellas", "Florida")) %>% 
  group_by(timestamp, county) %>% 
  summarize_all(sum) %>% 
  ungroup()
```


## Reported Positive Cases and Tests

The following table shows **new positive cases and tests**
with associated test positivity percentage for Hillsborough and Pinellas counties,
in addition to Florida in general.

These values are calculated based on the reported county-level confirmed cases and tests,
available at [Florida DOH's COVID-19 Data and Surveillance Dashboard][dashboard].
Note that these numbers are provisional and are based on cumulative county-level
testing and positive confirmed cases
and therefore may differ from a more detailed timeseries of daily testing.
Unfortunately, this is the closest approximation possible with publicly released data.

```{r pct_positive}
# pct_positive <- 
tampa_test_summary %>%
  select(timestamp:t_total) %>% 
  group_by(county) %>%
  arrange(timestamp) %>% 
  filter(t_positive > lag(t_positive)) %>%
  # Convert from cumulative to daily new
  mutate(
    daily_t_positive = t_positive - lag(t_positive),
    daily_t_total = t_total - lag(t_total)
  ) %>% 
  ungroup() %>% 
  filter(!is.na(daily_t_positive)) %>% 
  mutate(
    pct_positive = daily_t_positive / daily_t_total,
    day = strftime(timestamp, "%B__%d"),
    pct_positive = scales::percent(pct_positive, 1.1)
  ) %>% 
  mutate_at(vars(starts_with("daily")), format, big.mark = ',') %>% 
  mutate_at(vars(starts_with("t_")), format, big.mark = ',') %>% 
  filter(timestamp > today() - 10, timestamp < today()) %>% 
  # select(day, county, starts_with("daily"), pct_positive) %>%
  select(day, county, contains("t_"), pct_positive) %>%
  pivot_longer(-day:-county) %>% 
  pivot_wider(names_from = day, values_from = value) %>% 
  mutate(name = recode(
    name, 
    daily_t_positive = "New Positive", 
    daily_t_total = "New Total Tests", 
    pct_positive = "% Positive",
    t_positive = "Positive",
    t_total = "Total Tests"
  )) %>% 
  group_by(county) %>% 
  gt::gt() %>%
  gt::tab_header("New and Cumulative Positive and Total Tests") %>% 
  gt::cols_label(name = "") %>% 
  gt::tab_spanner_delim("__") %>%
  gt::tab_style(
    gt::cell_text(align = "right"),
    gt::cells_body(columns = contains("__"))
  ) %>% 
  gt::tab_style(
    gt::cell_fill(color = "#eeeeee"),
    gt::cells_body(rows = name == "% Positive")
  ) %>%
  gt::tab_style(
    gt::cell_borders(sides = "top", color = "#d8d8d8", weight = "2px"),
    gt::cells_body(rows = name == "New Positive")
  ) %>%
  gt::tab_style(
    gt::cell_text(weight = "bold"),
    gt::cells_row_groups()
  )
```

## Daily Changes

```{r daily-changes-in-testing}
tampa_test_summary %>% 
  select(day = timestamp, county, total = t_total, positive = t_positive, deaths) %>% 
  filter(!is.na(positive), !is.na(deaths)) %>% 
  arrange(day) %>% 
  group_by(county) %>% 
  mutate(
    positive = positive - lag(positive),
    total = total - lag(total),
    deaths = deaths - lag(deaths),
    complete = if_else(day == today(), "today", "past")
  ) %>% 
  filter(!is.na(positive)) %>% 
  ungroup() %>% 
  select(county, day, complete, positive, `total tests` = total, deaths) %>% 
  pivot_longer(cols = c(positive, `total tests`, deaths), names_to = "status") %>% 
  mutate_at(vars(status), tools::toTitleCase) %>% 
  mutate_at(vars(status), factor, levels = c("Total Tests", "Positive", "Deaths")) %>% 
  mutate_at(vars(day), lubridate::as_date) %>% 
  ggplot() +
  aes(day, value) +
  geom_col(aes(alpha = complete, fill = status)) +
  facet_wrap(~ status + county, scales = "free_y") +
  labs(
    x = NULL, y = NULL,
    caption = glue::glue(
      "Source: Florida DOH", 
      "Last update: {max(test_summary$timestamp)}",
      "github.com/gadenbuie/covid19-florida",
      .sep = "\n"
    )
  ) +
  scale_alpha_manual(
    values = c(past = 1, today = 0.33),
    guide = FALSE
  ) +
  scale_fill_manual(
    values = c("Total Tests" = "#63768d", Positive = "#ec4e20", Deaths = "#440154"), 
    guide = FALSE
  ) +
  theme_minimal(base_size = 14) +
  scale_x_date(date_breaks = "7 days", expand = expansion(add = 0.5), date_labels = "%b\n%d") +
  scale_y_continuous() +
  coord_cartesian(clip = "off") +
  theme(
    plot.margin = margin(0.5, 0.5, 0.5, 0.5, unit = "lines"),
    plot.subtitle = element_text(margin = margin(b = 1.25, unit = "lines")),
    plot.caption = element_text(color = "#444444"),
    panel.border = element_rect(color = "#dddddd", fill = NA),
    strip.text = element_text(face = "bold", margin = margin(b = 0.25, unit = "line")),
    axis.title.y = element_text(angle = 0, hjust = 1),
    # panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank()
  )
```


[dashboard]: https://fdoh.maps.arcgis.com/apps/opsdashboard/index.html#/8d0de33f260d444c852a615dc7837c86